Soss

### 2019-12-22 paper/paper.tex
code example
edits

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}

@@

@@

@@

>>>>

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}

@@

Here's some example code. Lots of dead space on the right, maybe want to try to keep code in a multi-column figure

\begin{lstlisting}[language = Julia]
  using Plots

  x = -3.0:0.01:3.0
  y = rand(length(x))
  plot(x, y)
\end{lstlisting}

@@

\begin{lstlisting}[language=julia]
struct Model{A,B,M} 
    args  :: Vector{Symbol}
    vals  :: NamedTuple
    dists :: NamedTuple
    retn  :: Union{Nothing, Symbol, Expr}
end
\end{lstlisting}

@@

\todo[inline]{Can Soss really generate arbitrary code?}
The ability to generate arbitrary  Julia code makes it difficult to measure performance in Soss. When a performance bottleneck is found, developers or users can ask Soss to generate something different. This design places no a priori constraints on performance.

\section{Extending Soss}
